Think again?\\ Optimal mental simulation tracks problem difficulty

### 2015-01-28 manuscript.tex
Add num participants analysis

\input{results/params.tex}
\input{results/corrs.tex}
\input{results/hole_empirical_analysis.tex}

@@

We recruited $N=328$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework. Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 6.5 minutes of work. Participants were randomly assigned to one of eight conditions, which determined which stimuli they judged based on a latin-square design (see Stimuli). Additionally, we excluded $N=8$ participants from analysis for answering incorrectly on more than one control trial (see Stimuli), leaving a total of $N=320$ participants.

@@

We recruited $N=60$ participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework. Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 5 minutes of work. Additionally, we excluded $N=18$ participants from analysis for failing to catch the ball on more than one control trial, leaving a total of $N=42$ participants.

>>>>

\input{results/params.tex}
\input{results/corrs.tex}
\input{results/hole_empirical_analysis.tex}
\input{results/num_participants.tex}

@@

We recruited \HoleNumComplete{} participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework. Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 6.5 minutes of work. Participants were randomly assigned to one of eight conditions, which determined which stimuli they judged based on a latin-square design (see Stimuli). Additionally, we excluded \HoleNumFailed{} participants from analysis for answering incorrectly on more than one control trial (see Stimuli), leaving a total of \HoleNumOk{} participants.

@@

We recruited \PaddleNumComplete{} participants on Amazon's Mechanical Turk using the psiTurk \cite{McDonnell12} experimental framework. Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for approximately 5 minutes of work. Additionally, we excluded \PaddleNumFailed{} participants from analysis for failing to catch the ball on more than one control trial, leaving a total of \PaddleNumOk{} participants.
